### 2011-08-01 doc/theses/mikula/analysis_of_recent_approaches.tex
Master thesis: In progress.

\chapter{Analysis of Recent Approaches}
\todo[inline]{Translate.}
Many approaches of XML Schema inference have been proposed. Most of them process XML data as an input for inference. Some of these methods are mentioned in this chapter.

Besides approaches exploiting XML data, approaches that utilize operations over XML data may be developed and they are of the most interest in terms of this work. According to my best knowledge at the time of writing there is just one approach of this category. It utilizes a set of XQuery queries to discover keys and foreign keys\todo{ref do literatury?}.

>>>>

\chapter{Analysis of Recent Approaches}
\todo[inline]{bibref na prehladovy clanok?}
Approaches of XML Schema inference can be divided by several criteria. Basic division is by language the resulting schema is written in. Commonly used languages are DTD and XML Schema.

The type of the inference method can be divided into \emph{heuristic} and \emph{grammar-inferring}. Heuristic methods are based on experience with manual construction of schemas and their result commonly does not belong to any class of grammar. On the contrary, result of the grammar-inferring methods belongs to a particular class of languages with specific characteristics.

Another important criterion is the type of input data. Most of the approaches process XML documents as the input of the inference process and the documents are valid against the resulting schema. Besides approaches exploiting XML data, approaches that utilize operations over XML data may be developed and they are the most significant approaches in terms of this work.

According to my best knowledge at the time of writing there is just one approach of this category. It utilizes a set of XQuery queries to discover keys and foreign keys\todo{ref do literatury?}.

\section{XML-Documents-utilizing Approaches}
The process of inference commonly used by a significant number of approaches can be summarized as the following: For each occurrence of element $e$ from the input XML documents and its subelements $e_1, e_2, ..., e_k$ a production $e \rightarrow e_1 e_2 ... e_k$ is constructed. The productions form so-called \emph{initial grammar} (IG). For each element type the productions are then merged, simplified and generalized using various methods and criteria. A common approach is so-called \emph{merging state algorithm}, where a \emph{prefix tree automaton} (PTA) is built from the productions of the same element type and the automaton is generalized via merging of its states. Finally, the generalized automaton/grammar is expressed in syntax of the respective XML schema language.

\subsection{XTRACT}
The XTRACT \todo{bibref} system is an example of \emph{heuristic} \emph{merging state algorithm} creating the result in DTD. Its process of inference consists of three steps:
\begin{enumerate}
\item Generalization - Generates a set of DTD candidates by searching the input for certain patterns and generalising corresponding parts using regular expressions.
\item Factoring - Groups of generalized candidate DTDs are factorized to a new ones by finding common sub-expressions to make them more concise.
\item Minimum Description Length (MDL) Principle - Selecting a near-optimal generalized DTD from the set of all generalized candidate DTDs.
\end{enumerate}

\todo[inline]{TODO}
